{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
removed todo
added remark about \sqcup
explained lift_k

The security levels in $LType$ are the security levels of the operands in the local state. To
express our security policy, we declare a function $\Gamma(x)$ that assigns to every variable
$x$ a security level. If we now want to \texttt{store} the top of the stack into the variable
$x$ one premise is that the security level of the program point ($se(i)$) \textit{and} the
security level of the value on top of the operand stack is \textit{lower or equal} to the
security level that was assigned by $\Gamma$ to the variable $x$. If this is the case the head
of $LType$ is removed.

The rule for the branching instruction can only be used if the security level of all program
points in the control dependence region are lower bounded by the security level of the value
that is used as the condition (i.e. the top of the operand stack). \todo{What does $lift_k$?}

@@

This type system is powerful enough to prevent explicit and implicit flows and can therefor
replace the type system defined previously. \todo{show ASSIGN rule?}

>>>>

The security levels in $LType$ are the security levels of the operands in the local state. To
express our security policy, we declare a function $\Gamma(x)$ that assigns to every variable
$x$ a security level. If we now want to \texttt{store} the top of the stack into the variable
$x$ one premise is that the security level of the program point ($se(i)$) \textit{and} the
security level of the value on top of the operand stack is \textit{lower or equal} to the
security level that was assigned by $\Gamma$ to the variable $x$. If this is the case the head
of $LType$ is removed. The $\sqcup$ operator is like a logical 'or', it returns the higher of
the given security values.

The rule for the branching instruction can only be used if the security level of all program
points in the control dependence region are lower bounded by the security level of the value
that is used as the condition (i.e. the top of the operand stack). The function $lift_k :
\text{Level} \rightarrow \text{Stack}(\text{Level}) \rightarrow \text{Stack}(\text{Level})$
extends $\sqcup$ to stacks of security levels. This ensures, that every program point in the control
dependence region has the same security level as the branching point.

@@

This type system is powerful enough to prevent explicit and implicit flows and can therefor
replace the type system defined previously.
